---
title: "APM1110 - FA 2 - Dacanay"
author: "Jordan Dacanay"
output: rmarkdown::github_document
---

### 1) Use R to illustrate that the probability of getting:
###(a) a head is 0.5 if a fair coin is tossed repeatedly;
#### Probability Table
```{r}
# NUmber of sample
n_sample <- 10000

# Simulate 100 coin tosses
print('Let Head = 1 and Tail = 0')
y <- sample (c(1, 0), n_sample, replace = TRUE)

# Probability Table
fair_coin_probability <- table(y)/n_sample
fair_coin_probability
```
#### Probability Plot
```{r}
num <- 1:n_sample
# Partial Probability
partial_events <- cumsum(y)
partial_probability <- partial_events / num

# Plot
plot(num, partial_probability, type = "l",
xlab = "Number of Toss", ylab = "Probability",
main = "Head Probability in Coin Toss")
abline(h=0.5, col="red")

# Add labels for each number of toss
hundredth_points <- seq(1000, max(num), by = 1000)
text(hundredth_points, partial_probability[hundredth_points], labels = hundredth_points, pos = 3)
points(hundredth_points, partial_probability[hundredth_points], col = "black", pch = 16)
```


###(b) a red card is 0.5 if cards are drawn repeatedly with replacement from a well-shuffled deck;
####Probability Table
```{r}
# Simulate 50 card draws
print('Let Red = 1 and Black = 0')

# Define the deck
deck <- c(rep(1, 26), rep(0, 26))
draws <- sample(deck, n_sample, replace = TRUE)

# Probability Table
red_card_probability <- table(draws)/n_sample
red_card_probability
```
#### Probability Plot
```{r}
num <- 1:n_sample
# Partial Probability
partial_events <- cumsum(draws)
partial_probability <- partial_events / num

# Plot
plot(num, partial_probability, type = "l",
xlab = "Number of Draws", ylab = "Probability",
main = "Red Card Probability in Drawing Cards")
abline(h=0.5, col="red")

# Add labels for each number of toss
text(hundredth_points, partial_probability[hundredth_points], labels = hundredth_points, pos = 3)
points(hundredth_points, partial_probability[hundredth_points], col = "black", pch = 16)
```


###(c) an even number is 0.5 if a fair die is rolled repeatedly.
####Probability Table
```{r}
# Simulate 50 die rolls
print('Let Even Numbers (2, 4, 6) = 1 and Odd Numbers (1, 3, 5) = 0')

# Define the deck
dice <- c(rep(1, 3), rep(0, 3))
rolls <- sample(dice, n_sample, replace = TRUE)

# Probability Table
fair_die_probability <- table(rolls)/n_sample
fair_die_probability
```
####Probability Plot
```{r}
num <- 1:n_sample
# Partial Probability
partial_events <- cumsum(rolls)
partial_probability <- partial_events / num

# Plot
plot(num, partial_probability, type = "l",
xlab = "Number of Rolls", ylab = "Probability",
main = "Probability of Even Number in Rolling a Die")
abline(h=0.5, col="red")

# Add labels for each number of toss
text(hundredth_points, partial_probability[hundredth_points], labels = hundredth_points, pos = 3)
points(hundredth_points, partial_probability[hundredth_points], col = "black", pch = 16)
```



### 2) An experiment consists of tossing two fair coins. Use R to simulate this experiment 100 times and obtain the relative frequency of each possible outcome. Hence, estimate the probability of getting one head and one tail in any order.
```{r}
# Generate Sample Spaces
states <- c("H", "T")
S <- expand.grid(states, states)
sample_spaces <- apply(S, 1, paste, collapse = "")

# Simulate 100 coin tosses
x <- sample(sample_spaces, 100, replace = TRUE)

# Calculate relative frequencies
coin_toss_probability <- table(x) / 100
print('Coin Toss Probability Table')
coin_toss_probability

# Probability of one head and one tail
probability_HT_TH <- coin_toss_probability["HT"] + coin_toss_probability["TH"]

# Print the combined probability
print('Probability of One Head and One tail')
probability_HT_TH

# Probability in percentage
print('Probability of One Head and One Tail in Percentage:')
print(sprintf("%.2f%%", probability_HT_TH * 100))
```



